---
title: "Developing Data Products Week 2 Assignment"
author: "Simon Grasdal"
date: "2025-01-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)

```

# Overview
Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and 
it must contain a map created with Leaflet. We would love to see you 
show off your creativity! 

# Code
This is a map of all the University athletics centers of participating 
Universities at the Ontario University Athletics Rowing Championships.
``` {r}
Centres <- data.frame(
        lat = c(44.353465,43.118263,45.5101457,43.2639397,
                46.3432694,43.9445322,44.2290438,44.2381073,43.533916,45.4196573,
                43.6627831,43.4656892,43.0189254,45.3858581),
        lng = c(-78.297777,-79.240137,-73.5812908,-79.9178252,-79.4916705,
                -78.8964374,-76.4949417,-76.4686244,-80.222941,-75.6775912,
                -79.4010326,-80.5423102,-81.2786109,-75.6950041), 
        name = c("Trent University", "Brock University", "McGill University",
                 "McMaster University", "Nipissing University", "Ontario Tech 
                 University", "Queens University", "Royal Military College", 
                 "University of Guelph", "University of Ottawa", "University of 
                 Toronto", "University of Waterloo", "Western University", 
                 "Carlton University" ))
my_map<-Centres %>% leaflet() %>% addTiles() %>% addMarkers(popup = Centres$name,
        clusterOptions = markerClusterOptions())
my_map

```
